HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units,
or {\it atomic}. In most cases, atomic units
correspond to individual words, but they may also correspond to unanalyzable
multi-word expressions.
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.

@@

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural. The labels assigned to such nodes reflect the extent to which
the relation between the sub-units is preserved in $t$.
\XXX{(BH: don't follow this) For instance, a Scene unit represents the relation between the
Scene elements, such as the predicate (main relation), participants and adverbials.}
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong.
We use a three label system with atomic units, as
opposed to a two label one in structural units,
as atomic units often have slight errors, in which cases we do want to provide partial credit.

There are many ways that the relationship between the children might go
wrong in translation

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
%\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units also in the
target language,
or {\it atomic}. In most cases, atomic units
correspond to individual words, but they may also correspond to unanalyzable
multi-word expressions.
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.

@@

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural.
% Ondrej thinks the following can be simply removed:
%The labels assigned to such nodes reflect the extent to which
%the relation between the sub-units is preserved in $t$.
%\XXX{(BH: don't follow this) For instance, a Scene unit represents the relation between the
%Scene elements, such as the predicate (main relation), participants and adverbials.}
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong.
We use a three label system with atomic units, as
opposed to a two label one in structural units,
as atomic units often have slight errors, in which cases we do want to provide partial credit.

There are many ways that the relationship between the children might go
wrong in translation:
